### 2008-03-21 trunk/Papers/dl-gre-08/bisim.tex

\section{Description Languages and Bisimulation} \label{sec:bisim}

The main point of this paper is to represent referring expressions
(REs) as formulas of description logic \cite{baad:desc03}.  In order
to make this point, we will now first define the two description
logics we will be working with -- \alc\ and \el.

@@

A key notion in studying description logics is \emph{bisimulation}.
We will discuss in detail the case for $\alc$; further details can be
found in~\cite{blac:moda01,kurt:expr99}.

\begin{definition}
Given a model $\gM = (\Delta^\gM,|\cdot|^\gM)$, two elements $i$ and
$i'$ of $\Delta^\gM$ are \emph{$\alc$-bisimilar} if there is a relation $Z
\subseteq \Delta^\gM \times \Delta^\gM$ such that 
\begin{itemize}
\item[i)] $(i,i') \in Z$.\\[-1.5em]
\item[ii)] if $(e_1, e_2) \in Z$ then $\propm(e_1) = \propm(e_2)$.\\[-1.5em]
\item[iii)] if $(e_1,e_2) \in Z$ and for some $R \in \rel$ there is $e_1'$ such that
$(e_1,e_1') \in |R|^\gM$ then there is $e_2'$ such that $(e_2,e_2') \in |R|^\gM$ and
$(e_1',e_2') \in Z$.\\[-1.5em]
\item[iv)] if $(e_1,e_2) \in Z$ and for some $R \in \rel$ there is $e_2'$ such that
$(e_2,e_2') \in |R|^\gM$ then there is $e_1'$ such that $(e_1,e_1') \in |R|^\gM$ and
$(e_1',e_2') \in Z$.
\end{itemize}
A maximal subset of $\Delta^\gM$ all of whose elements are pairwise
bisimilar is called an \emph{\alc-bisimulation class} of $\gM$.
\end{definition}

>>>>

\section{Description Logics and Simulation} \label{sec:bisim}

As we mentioned, in this paper we will represent referring expressions
(REs) as formulas of description logic~\cite{baad:desc03}.  In order
to make this point, we will now first define the two description
logics we will be working with -- \alc\ and \el.

@@

A key notion in studying description logics is \emph{simulation}.
We will discuss in detail the case for $\alc$; further details can be
found in~\cite{blac:moda01,kurt:expr99}.

\begin{definition}
Given a model $\gM = (\Delta^\gM,|\cdot|^\gM)$, two elements $i$ and
$i'$ of $\Delta^\gM$ are \emph{$\alc$-similar} if there is a relation $Z
\subseteq \Delta^\gM \times \Delta^\gM$ such that 
\begin{itemize}
\item[i)] $(i,i') \in Z$.\\[-1.5em]
\item[ii)] if $(e_1, e_2) \in Z$ then $\propm(e_1) = \propm(e_2)$.\\[-1.5em]
\item[iii)] if $(e_1,e_2) \in Z$ and for some $R \in \rel$ there is $e_1'$ such that
$(e_1,e_1') \in |R|^\gM$ then there is $e_2'$ such that $(e_2,e_2') \in |R|^\gM$ and
$(e_1',e_2') \in Z$.\\[-1.5em]
\item[iv)] if $(e_1,e_2) \in Z$ and for some $R \in \rel$ there is $e_2'$ such that
$(e_2,e_2') \in |R|^\gM$ then there is $e_1'$ such that $(e_1,e_1') \in |R|^\gM$ and
$(e_1',e_2') \in Z$.
\end{itemize}
A maximal subset of $\Delta^\gM$ all of whose elements are pairwise
bisimilar is called an \emph{\alc-bisimulation class} of $\gM$.
\end{definition}

### 2008-03-21 trunk/Papers/dl-gre-08/discussion.tex

Both the \el\ and the \alc\ algorithms took about 15 milliseconds to
compute distinguishing concepts for all 16 individuals in the Viethen
and Dale dataset.\footnote{We measured all runtimes on a MacBook Pro
  (Intel Core 2 Duo, 2.16 GHz) running Java 1.6 beta, and allowed the
  Java VM to warm up, i.e.\ just-in-time compile all bytecode, before
  taking the measurements.}

>>>>

Both the \el\ and the \alc\ algorithms took about 15 milliseconds to
compute distinguishing concepts for all 16 individuals in the Viethen
and Dale dataset.\footnote{Runtimes are meassured on a MacBook Pro
  (Intel Core 2 Duo, 2.16 GHz) running Java 1.6 beta, and we allowed the
  Java VM to warm up, i.e., just-in-time compile all bytecode, before
  taking the measurements.}

### 2008-03-21 trunk/Papers/dl-gre-08/related.tex

The approach presented here fits very well into this landscape, and in
a sense completes the picture by showing how to generate concepts for
arbitrary bisimulation classes in \alc, which combines all connectives
used in any of these previous approaches.  Where our approach breaks
new ground is in the way these concepts are computed: It successively
refines a decomposition of the domain into subsets.  In this way, it
is reminiscent of the Incremental Algorithm, and in fact the IA can be
seen as the special case of the \el\ algorithm for the non-relational
case.

>>>>

The approach presented here fits well into this landscape, and it completes the picture by showing how to generate concepts for
arbitrary bisimulation classes in \alc, which combines all connectives
used in any of these previous approaches.  Where our approach breaks
new ground is in the way these concepts are computed: It successively
refines a decomposition of the domain into subsets.  In this way, it
is reminiscent of the Incremental Algorithm, and in fact the IA can be
seen as the special case of the \el\ algorithm for the non-relational
case.
